Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-29 doc/gaia-chapter.tex
simplifying latex macros

\emph{Note: the abreviation \texttt{LT}, and the \texttt{fold LT} and \texttt{unfold LT} tactics,are not in \texttt{gaia}, but  have been added to make the goal display more readable.}

\inputsnippets{nfwfgaia/nfWfProofa}
We start with classic structural induction on \texttt{a}.

>>>>

\emph{Notes: the abbreviation \texttt{LT}, and the \texttt{fold LT} and \texttt{unfold LT} tactics,are not in \texttt{gaia}, but  have been added to make the goal display more readable.
The infix notation \texttt{`` \_ < \_''}  is bound to the order \texttt{T1lt} in \gaia, while,  in \Hydras,  it is bound to its restriction \texttt{LT} to terms in normal form. }

\inputsnippets{nfwfgaia/nfWfProofa}
We start with a classic structural induction on the type \texttt{T1}.
